---
title: "Homework11"
author: "Kendra Hodges"
date: "11/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. For this final lab exerise, use your newly-developed ggplot chops to create some nice graphs from your own data (If you do not have a good data frame to use for graphics, use one of the many built-in data frames from R (other than mpg, which we are using in class)). Experiment with different themes, theme base sizes, aesthetics, mappings, and faceting. When you are finished, try exporting them to high quality pdfs, jpgs, eps files, or other formats that you would use for submission to a journal.
```{r}

library(patchwork)

library(ggplot2)
library(ggthemes)

library(wesanderson)


# Creating A Scatter Plot in ggplot2
data(iris)
head(iris)
data <- iris
qplot(x=data$Sepal.Length, y=data$Petal.Length)
qplot(x=data$Sepal.Length, y=data$Petal.Length,
      geom=c("smooth", "point"))

plot1 <- ggplot(data=data, 
                mapping=aes(x=Sepal.Length,y=Petal.Length)) +
  geom_point(size=2,shape=21,color="black",fill=grey(0.4)) +
  labs(title= "My Scatter Plot",
     x ="Sepal Length",
     y= "Petal Length") +
  geom_smooth(method="lm", formula=y~x, color="black")

  
print(plot1)

plot1 + theme_base(base_size = 15, base_family = "serif")

### try to make a gradient scale!!!!

plot2 <- ggplot(data=data, 
                mapping=aes(x=Sepal.Length,y=Petal.Length, color=Petal.Length)) +
  geom_point() +
  labs(title= "My Scatter Plot",
     x ="Sepal Length",
     y= "Petal Length") +
  geom_smooth(method="lm", formula=y~x, color="black")
print(plot2)
plot2+theme_gray(base_size = 15, base_family = "serif") + scale_color_gradient(low="yellow",high="steelblue")


p1 <- ggplot(data,mapping=aes(x=Sepal.Length,y=Sepal.Width, fill=Species, color=Species)) +
  geom_point() + geom_smooth()
print(p1)

p3 <- ggplot(data=data,aes(x=Sepal.Length,y=Sepal.Width,group=Species))

p3 + geom_boxplot(fill=(gray(seq(from=0.5,to=0.9,length=3))))
# although it may not be that informative to show different colors in different boxplots


p4 <- ggplot(data,aes(x=Sepal.Length,y=Sepal.Width,fill=Species)) +
  geom_boxplot() +
  scale_fill_manual(values=wes_palettes[["Darjeeling1"]])
print(p4)
 # THIS ONE WORKED AND IS PRETTY GOOD!


# lets make one more graph using things from patchwork and such..
p5 <- ggplot(data,aes(x=Sepal.Length,y=Sepal.Width,fill=Species)) +
  geom_boxplot() + scale_fill_manual(values=wes_palettes[["Darjeeling1"]]) + geom_point(position=position_jitter(width=0.2,height=0.7), color="grey60")
print(p5)


```

