---
title: "Homework 5"
author: "Kendra Hodges"
date: "9/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(dplyr)
data(iris)
glimpse(iris)

str(iris)

head(iris)
tail(iris)


```

### 1.Examine the structure of the iris dataset. How many observations and variables are in the dataset?
  - 150 observations
  - 5 variables
  
  
### 2. Create a new data frame iris1 that contains only the species virginica and versicolor with sepal lengths longer than 6 cm and sepal widths longer than 2.5 cm. How many observations and variables are in the dataset?

```{r}
iris1 <- filter(iris, Species %in% c("virginica", "versicolor", Sepal.Length < 6, Sepal.Width > 2.5))
glimpse(iris1)

```
  - 100 Observations
  - 5 Variables


### 3. Now, create a iris2 data frame from iris1 that contains only the columns for Species, Sepal.Length, and Sepal.Width. How many observations and variables are in the dataset?

```{r}
iris2 <- select(iris1, Species, Sepal.Length, Sepal.Width)
glimpse(iris2)

```
 - 100 Observations
 - 3 Variables

### 4. Create an iris3 data frame from iris2 that orders the observations from largest to smallest sepal length. Show the first 6 rows of this dataset.

```{r}

iris3 <- arrange(iris2, desc(Sepal.Length))
head(iris3)
  
```
### 5. Create an iris4 data frame from iris3 that creates a column with a sepal area (length * width) value for each observation. How many observations and variables are in the dataset?

```{r}

iris4 <- mutate(iris3, area = Sepal.Length * Sepal.Width)
glimpse(iris4)
  
```
 - 100 Observations
 - 4 Variables
 
### 6. Create iris5 that calculates the average sepal length, the average sepal width, and the sample size of the entire iris4 data frame and print iris5.

```{r}
iris5 <- summarize(iris4, meanLength = mean(Sepal.Length), meanWidth = mean(Sepal.Width), n())
print(iris5)
```

### 7. Finally, create iris6 that calculates the average sepal length, the average sepal width, and the sample size for each species of in the iris4 data frame and print iris6.

```{r}
iris6 <- group_by(iris4, Species)
  summarize(iris4, meanLength = mean(Sepal.Length), meanWidth = mean(Sepal.Width), n())
print(iris6)

```




