---
title: "Homework10"
author: "Kendra Hodges"
date: "10/31/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Using a for loop, write  function to calculate the number of zeroes ina numeric vector. Before entering the loop, set up a counter variable counter<- 0. inside the loop, add 1 to counter each time youhave a zero in the matric. Finall,y use return(counter) for the output.
```{r}
myVec <- sample(-5:5, size = 10, replace = TRUE)

countZeros <- function(myVec2=myVec) {
  counter <- 0
  for(i in seq_along(myVec2)){
    if(myVec2[i]==0) counter <- (counter+1)}

    return(counter)
}

countZeros()


```
### 2. Use subsetting instead of a loop to rewrite the function as a single line of code.
```{r}
length(which(myVec ==0))
```

### 3.Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.
```{r}

myMatrix <- function(x=5,y=6) {
  mat1 <- matrix(nrow=x, ncol=y)
  for(i in 1:nrow(mat1)){
    for(j in 1:ncol(mat1)){
      mat1[i,j] <- i*j
    }
  }
  return(mat1)
}

myMatrix()
  
```
### 4. Use the code from yesterday’s class to design and conduct a randomization test for some of your own data. You will need to modify the functions that read in the data, calculate the metric, and randomize the data. Once those are set up, the program should run correctly calling your new functions. Also, to make your analysis fully repeatable, make sure you set the random number seed at the beginning (use either set.seed() in base R, or char2seed in the TeachingDemos package
```{r}
#set seet
#global variables
library(ggplot2)
#read data
 readData <- function()
#calculate the metric
  getMetric <- function()
# create randomization
    shuffleData <- function()
# calculate p value from simulated metrics
      getPVAL <- function()

```
### 5.For comparison, calculate in R the standard statistical analysis you would use with these data. How does the p-value compare for the standard test versus the p value you estimated from your randomization test? If the p values seem very different, run the program again with a different starting seed (and/or increase the number of replications in your randomization test). If there are persistent differences in the p value of the standard test versus your randomization, what do you think is responsible for this difference?

```{r}

```




