---
title: "Homework6"
author: "Kendra Hodges"
date: "10/3/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
z <- read.table("MyDataFile.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)
```
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

```{r}
# quick and dirty, a truncated normal distribution to work on the solution set

z <- rnorm(n=200,mean=2)
z <- data.frame(1:200,z)
names(z) <- list("ID","Height")

z <- z[z$Height>0,]
str(z)
summary(z$Height)
```
# Creating a Histogram
```{r}
p1 <- ggplot(data=z, aes(x=Height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

## Empirical Density Curve
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```

## Maximum likelihood parameters for normal 
```{r}
normPars <- fitdistr(z$Height,"normal")
print(normPars)

str(normPars)
normPars$estimate["mean"]
```

## Normal Probabilty Density Curve
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Height),len=length(z$Height))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Height), args = list(mean = meanML, sd = sdML))
 p1 + stat
```

## Exponential Curve
```{r}
expoPars <- fitdistr(z$Height,"exponential")

rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$Height), args = list(rate=rateML))
 p1 + stat + stat2
```

## Uniform Probabilty Curve
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$Height), args = list(min=min(z$Height), max=max(z$Height)))
 p1 + stat + stat2 + stat3
```

## Gamma Probabilty Curve
```{r}
gammaPars <- fitdistr(z$Height,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$Height), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

## Beta Probabilty Curve
```{r}
pSpecial <- ggplot(data=z, aes(x=Height/(max(Height + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$Height/max(z$Height + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$Height), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

```

## Normal Distribution is the best fit!
### maximum likelihood parameters
```{r}
normPars <- fitdistr(z$Height, "normal")
print(normPars)
```
### simulated data set
```{r}
z <- rnorm(n=200,mean=2.0897)
z <- data.frame(1:200,z)
names(z) <- list("ID","Height")
z <- z[z$Height>0,]
str(z)
summary(z$Height)
```

### Histogram of simulated data set
```{r}
p1 <- ggplot(data=z, aes(x=Height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

### add probability density curve
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Height),len=length(z$Height))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Height), args = list(mean = meanML, sd = sdML))
 p1 + stat

```

###histogram plot of the original data, and also include the probability density curve
```{r}
z <- read.table("MyDataFile.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
z <- rnorm(n=200,mean=2)
z <- data.frame(1:200,z)
names(z) <- list("ID","Height")

z <- z[z$Height>0,]

p1 <- ggplot(data=z, aes(x=Height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 

meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Height),len=length(z$Height))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Height), args = list(mean = meanML, sd = sdML))
 p1 + stat

```

## How do they differ?
The simulated data set graph was best reprsented by the normal distriubtion curve however when i recreated the graph using the original data and then added in the normal probabilty density curve it was not the best fitting distribution. I think the gamma distribution probably would have been a better fit for this graph.

