---
title: "Homework 7"
author: "Kendra Hodges"
date: "10/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating Fake Data Set
```{r}
library(tidyverse)

ngroup <- 2
nName <- c("Control","Treatment")
nSize <- c(17,20)
nMean <- c(30.3,20.3)
nSD <- c(3,3)

ID <- 1:(sum(nSize))

freq <- c(rnorm(n=nSize[1], mean=nMean[1],sd=nSD[1]), 
         rnorm(n=nSize[2], mean=nMean[2],sd=nSD[2]))
variable<- rep(nName,nSize)
table(variable)
ANOdata <- data.frame(ID,variable,freq)
str(ANOdata)

head(ANOdata)

ANOmodel <- aov(freq~variable,data=ANOdata)
print(ANOmodel)
z <- summary(ANOmodel)
str(z)
unlist(z)
ANOsum <- list(Fval=unlist(z)[7],probF=unlist(z)[9])
ANOsum
```
the values used for the mean, sample size, and variances produced significant values. After running this analysis several times, each time it generated a p value > 0.05 


## Creating boxplot for data
```{r}
ANOPlot <- ggplot(data=ANOdata,
                  aes(x=variable,y=freq,
                      fill=variable)) +
  geom_boxplot()
print(ANOPlot)

```

## Adjusting the means of different groups
### Same mean values

```{r}
library(tidyverse)

ngroup <- 2
nName <- c("Control","Treatment")
nSize <- c(17,20)
nMean <- c(30,30)
nSD <- c(3,3)

ID <- 1:(sum(nSize))

freq <- c(rnorm(n=nSize[1], mean=nMean[1],sd=nSD[1]), 
         rnorm(n=nSize[2], mean=nMean[2],sd=nSD[2]))
variable<- rep(nName,nSize)
table(variable)
ANOdata <- data.frame(ID,variable,freq)
str(ANOdata)

head(ANOdata)

ANOmodel <- aov(freq~variable,data=ANOdata)
print(ANOmodel)
z <- summary(ANOmodel)
str(z)
unlist(z)
ANOsum <- list(Fval=unlist(z)[7],probF=unlist(z)[9])

ANOPlot <- ggplot(data=ANOdata,
                  aes(x=variable,y=freq,
                      fill=variable)) +
  geom_boxplot()
print(ANOPlot)
```
Running this analysis with equal mean values generated mostly insignificant p values (< 0.05)

### Different mean values to generate a significant pvalue
```{r}
library(tidyverse)

ngroup <- 2
nName <- c("Control","Treatment")
nSize <- c(17,20)
nMean <- c(15,30)
nSD <- c(3,3)

ID <- 1:(sum(nSize))

freq <- c(rnorm(n=nSize[1], mean=nMean[1],sd=nSD[1]), 
         rnorm(n=nSize[2], mean=nMean[2],sd=nSD[2]))
variable<- rep(nName,nSize)
table(variable)
ANOdata <- data.frame(ID,variable,freq)
str(ANOdata)

head(ANOdata)

ANOmodel <- aov(freq~variable,data=ANOdata)
print(ANOmodel)
z <- summary(ANOmodel)
str(z)
unlist(z)
ANOsum <- list(Fval=unlist(z)[7],probF=unlist(z)[9])

ANOPlot <- ggplot(data=ANOdata,
                  aes(x=variable,y=freq,
                      fill=variable)) +
  geom_boxplot()
print(ANOPlot)
```
Running this analysis with mean values that differed by 15 generated  singificant pvalues. The closer the mean values are to one another, the less likely it is to obtain a signficant pvalue. 

## Adjusting sample size

```{r}
library(tidyverse)

ngroup <- 2
nName <- c("Control","Treatment")
nSize <- c(5,5) 
nMean <- c(30.3,20.3)
nSD <- c(3,3)

ID <- 1:(sum(nSize))

freq <- c(rnorm(n=nSize[1], mean=nMean[1],sd=nSD[1]), 
         rnorm(n=nSize[2], mean=nMean[2],sd=nSD[2]))
variable<- rep(nName,nSize)
table(variable)
ANOdata <- data.frame(ID,variable,freq)
str(ANOdata)

head(ANOdata)

ANOmodel <- aov(freq~variable,data=ANOdata)
print(ANOmodel)
z <- summary(ANOmodel)
str(z)
unlist(z)
ANOsum <- list(Fval=unlist(z)[7],probF=unlist(z)[9])
ANOsum

## When adjusting the sample size it always generate a statistically signficant effect. This may due to my dataset being relatively small.
```

# Boxplots with adjusted sample size
```{r}
ANOPlot <- ggplot(data=ANOdata,
                  aes(x=variable,y=freq,
                      fill=variable)) +
  geom_boxplot()
print(ANOPlot)
```

## Adjusting variances 

```{r}
library(tidyverse)

ngroup <- 2
nName <- c("Control","Treatment")
nSize <- c(17,20) 
nMean <- c(30.3,20.3)
nSD <- c(2,2)

ID <- 1:(sum(nSize))

freq <- c(rnorm(n=nSize[1], mean=nMean[1],sd=nSD[1]), 
         rnorm(n=nSize[2], mean=nMean[2],sd=nSD[2]))
variable<- rep(nName,nSize)
table(variable)
ANOdata <- data.frame(ID,variable,freq)
str(ANOdata)

head(ANOdata)

ANOmodel <- aov(freq~variable,data=ANOdata)
print(ANOmodel)
z <- summary(ANOmodel)
str(z)
unlist(z)
ANOsum <- list(Fval=unlist(z)[7],probF=unlist(z)[9])
ANOsum

```



# Boxplots with adjusted variances
```{r}
ANOPlot <- ggplot(data=ANOdata,
                  aes(x=variable,y=freq,
                      fill=variable)) +
  geom_boxplot()
print(ANOPlot)
```
